---
title: "Replication of Fluency and the Detection of Misleading Questions: Low Processing Fluency Attenuates The Moses Illusion by Hyunjin Song & Norbert Schwarz (2008, Social Cognition)"
author: "Ashley Monteiro (asmonteiro@ucsd.edu)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Replication reports should all use this template to standardize reporting across projects.  These reports will be public supplementary materials that accompany the summary report(s) of the aggregate results. -->

## Introduction

[No abstract is needed.]  Each replication project will have a straightforward, no frills report of the study and results.  These reports will be publicly available as supplementary material for the aggregate report(s) of the project as a whole.  Also, to maximize project integrity, the intro and methods will be written and critiqued in advance of data collection.  Introductions can be just 1-2 paragraphs clarifying the main idea of the original study, the target finding for replication, and any other essential information.  It will NOT have a literature review -- that is in the original publication. You can write both the introduction and the methods in past tense.  

https://github.com/ashleybellmonteiro/song2008

As a researcher interested in social psychology I found the paper, "Fluency and the Detection of Misleading Questions: Low Processing Fluency Attenuates The Moses Illusion" to be particularly interesting. Although I am primarily an emotion researcher, I enjoy incorporating topics such as user experience, social media, and fluency effects into my work. A big reason I chose this paper was because I don't have much experience in this exact type of work. Instead of doing studies that I will run all the time, I've decided to use this project as an opportunity to try something new. By engaging in this research I hope to not only broaden my understanding of cognitive processes, but also enrich my upcoming research...especially my first year project! 

The stimuli and procedures I need for the pretest would all be online, possibly done over Qualtrics. I would first test both the font type and color to see how/if they affect reading ease. This would be done by using five undergraduates per each condition. One sentence will be printed in grey brush script while the other in black Arial. They would rate on a scale of 1-7 the ease in which they could read the text. 1 being very difficult 7 being very easy. When it comes to the main experiment I would recruit 32 more undergrads and randomly assign them to either the easy to read or difficult to read conditions. Then I will have them both read and answer a couple of trivia questions correlating with their given group, easy or difficult to read. The first question would be a control question while the second question would be the distroted question. 

A potential challenge of this study may be the trivia questions that were used as stimuli in the previous experiment. My worry is that people may not understand them. Other than that though, I am quite confident this experiment will run smoothly. However, something that may be challenging for me would be R, just because I am so new to coding. 

## Methods

### Power Analysis

Original effect size, power analysis for samples to achieve 80%, 90%, 95% power to detect that effect size.  Considerations of feasibility for selecting planned sample size.

### Planned Sample

Planned sample size and/or termination rule, sampling frame, known demographics if any, preselection rules if any.

### Materials

All materials - can quote directly from original article - just put the text in quotations and note that this was followed precisely.  Or, quote directly and just point out exceptions to what was described in the original article.

### Procedure	

Can quote directly from original article - just put the text in quotations and note that this was followed precisely.  Or, quote directly and just point out exceptions to what was described in the original article.

### Analysis Plan

Can also quote directly, though it is less often spelled out effectively for an analysis strategy section.  The key is to report an analysis strategy that is as close to the original - data cleaning rules, data exclusion rules, covariates, etc. - as possible.  

**Clarify key analysis of interest here**  You can also pre-specify additional analyses you plan to do.

### Differences from Original Study

Explicitly describe known differences in sample, setting, procedure, and analysis plan from original study.  The goal, of course, is to minimize those differences, but differences will inevitably occur.  Also, note whether such differences are anticipated to make a difference based on claims in the original article or subsequent published research on the conditions for obtaining the effect.

### Methods Addendum (Post Data Collection)

You can comment this section out prior to final report with data collection.

#### Actual Sample
  Sample size, demographics, data exclusions based on rules spelled out in analysis plan

#### Differences from pre-data collection methods plan
  Any differences from what was described as the original plan, or “none”.


## Results


### Data preparation

Data preparation following the analysis plan.
	
```{r include=F}
### Data Preparation

#### Load Relevant Libraries and Functions

#### Import data

#### Data exclusion / filtering

#### Prepare data for analysis - create columns etc.
```

### Confirmatory analysis

The analyses as specified in the analysis plan.  

*Side-by-side graph with original graph is ideal here*

### Exploratory analyses

Any follow-up analyses desired (not required).  

## Discussion

### Summary of Replication Attempt

Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.  

### Commentary

Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt.  None of these need to be long.
